A Plot is Worth a Thousand Tests: Assessing Residual Diagnostics with the Lineup Protocol

### 2023-04-23 paper.Rmd
revised 4.1.3 more, in light of big changes needed in 4.2

\noindent We would expect that structure in residual plots would be easier to perceive when the fitted values are uniformly distributed.

Three different sample sizes were used in our experiment: $n = 50, 100, 300$. We expect considerable variation in the signal strength in the simulated data plots with smaller $n$. A sample size of 300 is typically enough for structure to be visible in a scatter plot reliably. Beyond 300, structure can be obscured by over-plotting, and a different type of display that included transparency, binning or density mapping, might be needed.

>>>>

\noindent Figure \ref{fig:different-dist} shows the non-linear pattern, a "U" shape, with the different fitted value distributions. We would expect that structure in residual plots would be easier to perceive when the fitted values are uniformly distributed.

Three different sample sizes were used in our experiment: $n = 50, 100, 300$. Figure \ref{fig:different-n} shows the non-linear "S" shape for different sample sizes. We expect signal strength to decline in the simulated data plots with smaller $n$. A sample size of 300 is typically enough for structure to be visible in a scatter plot reliably. Beyond 300, structure can be obscured by over-plotting, and a different type of display that included transparency, binning or density mapping, might be needed.

### 2023-04-23 paper.tex
revised 4.1.3 more, in light of big changes needed in 4.2

\noindent We would expect that structure in residual plots would be
easier to perceive when the fitted values are uniformly distributed.

Three different sample sizes were used in our experiment:
\(n = 50, 100, 300\). We expect considerable variation in the signal
strength in the simulated data plots with smaller \(n\). A sample size
of 300 is typically enough for structure to be visible in a scatter plot
reliably. Beyond 300, structure can be obscured by over-plotting, and a
different type of display that included transparency, binning or density
mapping, might be needed.

>>>>

\noindent Figure \ref{fig:different-dist} shows the non-linear pattern,
a ``U'' shape, with the different fitted value distributions. We would
expect that structure in residual plots would be easier to perceive when
the fitted values are uniformly distributed.

Three different sample sizes were used in our experiment:
\(n = 50, 100, 300\). Figure \ref{fig:different-n} shows the non-linear
``S'' shape for different sample sizes. We expect signal strength to
decline in the simulated data plots with smaller \(n\). A sample size of
300 is typically enough for structure to be visible in a scatter plot
reliably. Beyond 300, structure can be obscured by over-plotting, and a
different type of display that included transparency, binning or density
mapping, might be needed.
